### 2023-01-20 code/plots.Rmd
replaced figures

all_sim |> 
  group_by(rep, type) |>
  filter(t==max(t), species=="X", rep < 10) |>
  ggplot(aes(rep, cumulative_reward)) + 
    geom_col()  + 
    facet_wrap(~type) + 
    labs(y = "reward", x = "repetition")

@@

```{r}
p1 <- all_sim |> 
  group_by(rep, type) |>
  filter(rep == 0) |>
  ggplot(aes(t, abundance, col = species)) + 
    geom_line()  + 
    facet_wrap(~type) + 
    labs(y = "reward", x = "repetition")

>>>>

all_sim |> 
    mutate(across(type, factor, levels = c("Opt const mortality", "80% opt const mortality", 
                                           "DRL"))) |>
    group_by(rep, type) |>
    filter(t==max(t), species=="X", rep < 10) |>
    ggplot(aes(rep, cumulative_reward)) + 
        geom_col()  + 
        facet_wrap(~type) + 
        labs(y = "reward", x = "repetition")

@@

```{r}
all_sim |> 
    mutate(across(type, factor, levels = c("Opt const mortality", "80% opt const mortality", 
                                           "DRL"))) |>
    group_by(rep, type) |>
    filter(rep == 0) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        facet_wrap(~type) + 
        labs(y = "reward", x = "repetition")
all_sim |>
    group_by(rep,type) |>
    filter(rep<10) |>
    ggplot(aes(t, action)) + 
    geom_line()  + 
    facet_wrap(~type) + 
    labs(y = "action", x = "repetition")
